From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-07 Pi+/paper/finite.tex
Align fig 3
Resize braid diagrams

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\Huge] at (1.75, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (1.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.5, 0)
      {braid={ 1, s_1 }};
      \node[font=\Huge] at (3, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (4, 0)
      {braid={ 1, s_1}};
      \node[] at (5.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (5.5, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\Huge] at (2.15, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (3, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    % https://q.uiver.app/?q=WzAsNixbMSwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzIsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMSwzLCJcXHRhdV8xIl0sWzIsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        & {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} && {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} && {\tau_2\tau_2\tau_1} \\
        & {\tau_1}
        \arrow["\braid"', squiggly, from=1-2, to=2-1]
        \arrow["\braid", squiggly, from=1-2, to=2-3]
        \arrow["\cancel"', squiggly, from=2-1, to=3-1]
        \arrow["\cancel"', squiggly, from=3-1, to=4-2]
        \arrow["\cancel", squiggly, from=2-3, to=3-3]
        \arrow["\cancel", squiggly, from=3-3, to=4-2]
      \end{tikzcd}
    }
    \caption{Converging critical pairs}
    \label{fig:critical-pairs-converging}
  \end{subfigure}
  \begin{subfigure}[b]{0.50\textwidth}
    \adjustbox{scale=\scalef,center}{
    % https://q.uiver.app/?q=WzAsMyxbMSwwLCJcXHRhdV8zXFx0YXVfMlxcdGF1XzNcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMlxcdGF1XzNcXHRhdV8yXFx0YXVfMSJdLFszLDEsIlxcdGF1XzNcXHRhdV8yXFx0YXVfMVxcdGF1XzMiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiYnJhaWQiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFsyLDEsIlxcbG9uZ2JyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
    \begin{tikzcd}
      & {\tau_3\tau_2\tau_3\tau_1} \\
      &&& {\tau_3\tau_2\tau_1\tau_3} \\
      {\tau_2\tau_3\tau_2\tau_1}
      \arrow["braid"', squiggly, from=1-2, to=3-1]
      \arrow["braid", squiggly, from=1-2, to=2-4]
      \arrow["\longbraid", squiggly, from=2-4, to=3-1]
    \end{tikzcd}
    }
    \caption{A non-converging critical pair in $\cox*$ converging in $\longcox*$}
    \label{fig:critical-pairs-non-converging}
  \end{subfigure}

@@

The result of this function is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\). Since we think of the
number $m$ as the transposition swapping elements $(\el{m}, \el{m+1})$, the role of this helper function
is to produce a sequence of transpositions -- a permutation -- which moves element $\el{k + n}$ by $k$ places left,
shifting all the elements in between one place right (see~\Cref{fig:downf}).

\begin{figure}
  \[
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 5,
        width = 0.6cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick]
      {braid={s_1, s_2, s_3, s_4}};
    \end{tikzpicture}
  \]
  \caption{Braiding diagram for $0 \downf 4$}
  \label{fig:downf}
\end{figure}

Then, the directed relation $\longcox$ is defined with the following generators.

\begin{definition}[$\longcox$]
  \begin{align*}
    \longcancel
     & : \forall n, l, r \to (l \append n \cons n \cons r) \longcox (l \append r)                                                                   \\
    \longswap
     & : \forall k, n, l, r \to (\suc[k] < n) \to (l \append n \cons k \cons r) \longcox (l \append k \cons n \append r)                            \\
    \longbraid
     & : \forall n, l, r \to (l \append (n \downf 2 + k) \append (1 + k + n) \cons r) \longcox (l \append (k + n) \cons (n \downf 2 + k) \append r)
  \end{align*}
\end{definition}

@@

\begin{figure}
  \begin{tikzpicture}
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (0, 0)
    {braid={s_5, s_1, s_2, s_3, s_4, s_5}};
    \node[font=\Huge] at (4, 1.3) {\(\rightarrow\)};
    \pic[local bounding box=my braid,braid/.cd,
      number of strands = 6,
      width = 0.6cm,
      height = 0.4cm,
      border height = 0.1cm,
      thick] at (5, 0)
    {braid={s_1, s_2, s_3, s_4, s_5, s_4}};
  \end{tikzpicture}
  \caption{Braiding diagram for $\longbraid$ with $n = 0$ and $k = 3$}
  \label{fig:longcox}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    % https://q.uiver.app/?q=WzAsNixbMSwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzIsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMSwzLCJcXHRhdV8xIl0sWzIsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        & {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} && {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} && {\tau_2\tau_2\tau_1} \\
        & {\tau_1}
        \arrow["\braid"', squiggly, from=1-2, to=2-1]
        \arrow["\braid", squiggly, from=1-2, to=2-3]
        \arrow["\cancel"', squiggly, from=2-1, to=3-1]
        \arrow["\cancel"', squiggly, from=3-1, to=4-2]
        \arrow["\cancel", squiggly, from=2-3, to=3-3]
        \arrow["\cancel", squiggly, from=3-3, to=4-2]
      \end{tikzcd}
    }
    \caption{A converging critical pair in $\cox*$}
    \label{fig:critical-pairs-converging}
  \end{subfigure}
  \begin{subfigure}[b]{0.55\textwidth}
    \adjustbox{scale=\scalef,center}{
      % https://q.uiver.app/?q=WzAsMyxbMSwwLCJcXHRhdV8zXFx0YXVfMlxcdGF1XzNcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMlxcdGF1XzNcXHRhdV8yXFx0YXVfMSJdLFszLDEsIlxcdGF1XzNcXHRhdV8yXFx0YXVfMVxcdGF1XzMiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiYnJhaWQiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFsyLDEsIlxcbG9uZ2JyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
      \begin{tikzcd}
        & {\tau_3\tau_2\tau_3\tau_1} \\
        &&& {\tau_3\tau_2\tau_1\tau_3} \\
        {\tau_2\tau_3\tau_2\tau_1}
        \arrow["braid"', squiggly, from=1-2, to=3-1]
        \arrow["braid", squiggly, from=1-2, to=2-4]
        \arrow["\longbraid", squiggly, from=2-4, to=3-1]
      \end{tikzcd}
    }
    \caption{A non-converging critical pair in $\cox*$ converging in $\longcox*$}
    \label{fig:critical-pairs-non-converging}
  \end{subfigure}

@@

The result of this function is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\). Since we think of the
number $m$ as the transposition swapping elements $(\el{m}, \el{m+1})$, the role of this helper function is to produce a
sequence of transpositions -- a permutation -- which moves element $\el{k + n}$ by $k$ places left, shifting all the
elements in between one place right (see~\Cref{fig:downf}). Then, the directed relation $\longcox$ is defined with the
following generators.

\begin{definition}[$\longcox$]
  \begin{align*}
    \longcancel
     & : \forall n, l, r \to (l \append n \cons n \cons r) \longcox (l \append r)                                                                      \\
    \longswap
     & : \forall n, k, l, r \to (\suc[k] < n) \to (l \append n \cons k \cons r) \longcox (l \append k \cons n \append r)                               \\
    \longbraid
     & : \forall n, k, l, r \to (l \append (n \downf 2 + k) \append (1 + k + n) \cons r) \longcox (l \append (k + n) \cons (n \downf 2 + k) \append r)
  \end{align*}
\end{definition}

@@

\begin{figure}
  \begin{subfigure}[b]{0.3\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 7,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick]
      {braid={s_1, s_2, s_3, s_4, s_5, s_6}};
    \end{tikzpicture}
    \caption{$0 \downf 6$}
    \label{fig:downf}
  \end{subfigure}
  \begin{subfigure}[b]{0.6\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 6,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={s_5, s_1, s_2, s_3, s_4, s_5}};
      \node[font=\large] at (3, 1.3) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 6,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (4, 0)
      {braid={s_1, s_2, s_3, s_4, s_5, s_4}};
    \end{tikzpicture}
    \caption{$\longbraid$ with $n = 0$ and $k = 3$}
    \label{fig:longcox}
  \end{subfigure}
  \caption{Braiding diarams for modified Coxeter relations.}
  \label{fig:coxeter-braid-mod}
\end{figure}
